%!TEX program = xelatex

\documentclass[11pt,letterpaper]{article}

\def\myauthor{Daniel Rothenberg}
\def\mytitle{vita}
\def\myemail{darothen@mit.edu}
\def\mytwitter{danrothenberg}
\def\mywebsite{http://www.danielrothenberg.com}
\def\mywebsiteshort{danielrothenberg.com}
\def\myphone{(502) 648-7513}
\def\mykeywords{}

\setlength\parindent{0pt}

\newenvironment{itemize*}%
{\begin{itemize}%
  \setlength{\itemsep}{0pt}}%
{\end{itemize}}

\usepackage{comment}
\usepackage{url}
\usepackage{fancyhdr}
\usepackage{lastpage}
%\usepackage{ocgtools}
\usepackage{enumitem}
\setlist{nolistsep,leftmargin=0.15in}
\usepackage[log-declarations=false]{xparse}
\usepackage{fontspec}
\usepackage{microtype}
\usepackage[margin=0.8in,right=.75in,left=1.5in]{geometry}
\usepackage[strict]{changepage}
\usepackage[
  ocgcolorlinks,
  urlcolor={[rgb]{0,0,0.54}},
  unicode,
  plainpages=false,
  pdfpagelabels,
  pdftitle={\mytitle},
  pdfauthor={\myauthor},
  pdfkeywords={\mykeywords}
]{hyperref}
\usepackage{fontawesome}

% fix ocgcolor link breaking; thanks due to Benjamin Lerner (http://goo.gl/VZKR7M)
\makeatletter
\AtBeginDocument{%
  \newlength{\temp@x}%
  \newlength{\temp@y}%
  \newlength{\temp@w}%
  \newlength{\temp@h}%
  \def\my@coords#1#2#3#4{%
    \setlength{\temp@x}{#1}%
    \setlength{\temp@y}{#2}%
    \setlength{\temp@w}{#3}%
    \setlength{\temp@h}{#4}%
    \adjustlengths{}%
    \my@pdfliteral{\strip@pt\temp@x\space\strip@pt\temp@y\space\strip@pt\temp@w\space\strip@pt\temp@h\space re}}%
  \ifpdf
    \typeout{In PDF mode}%
    \def\my@pdfliteral#1{\pdfliteral page{#1}}% I don't know why % this command...
    \def\adjustlengths{}%
  \fi
  \ifxetex
    \def\my@pdfliteral #1{\special{pdf: literal direct #1}}% isn't equivalent to this one
    \def\adjustlengths{\setlength{\temp@h}{-\temp@h}\addtolength{\temp@y}{1in}\addtolength{\temp@x}{-1in}}%
  \fi%
  \def\Hy@colorlink#1{%
    \begingroup
      \ifHy@ocgcolorlinks
        \def\Hy@ocgcolor{#1}%
        \my@pdfliteral{q}%
        \my@pdfliteral{7 Tr}% Set text mode to clipping-only
      \else
        \HyColor@UseColor#1%
      \fi
  }%
  \def\Hy@endcolorlink{%
    \ifHy@ocgcolorlinks%
      \my@pdfliteral{/OC/OCPrint BDC}%
      \my@coords{0pt}{0pt}{\pdfpagewidth}{\pdfpageheight}%
      \my@pdfliteral{F}% Fill clipping path (the url's text) with current color
      \my@pdfliteral{EMC/OC/OCView BDC}%
      \begingroup%
        \expandafter\HyColor@UseColor\Hy@ocgcolor%
        \my@coords{0pt}{0pt}{\pdfpagewidth}{\pdfpageheight}%
        \my@pdfliteral{F}% Fill clipping path (the url's text) with \Hy@ocgcolor
      \endgroup%
      \my@pdfliteral{EMC}%
      \my@pdfliteral{0 Tr}% Reset text to normal mode
      \my@pdfliteral{Q}%
    \fi
    \endgroup
  }%
}
\makeatother
% end fixes

\newcommand{\ML}{\textsc{Matlab}}
\newcommand{\Simu}{Simulink}
\newcommand{\MLS}{\ML{}/\Simu{}}
\newcommand{\apdl}{\textsc{APDL}}
\newcommand{\ansys}{\textsc{Ansys}}
\newcommand{\fluent}{\textsc{Fluent}}
\newcommand\CPP{C/C\ensuremath{+}\ensuremath{+}}
\newcommand{\Star}{\textsc{Star-CCM\ensuremath{+}}}

\newcommand{\mhead}[1]{\leavevmode\marginpar{\sffamily\footnotesize #1}}
\newcommand{\rdate}[1]{{\addfontfeature{Numbers=OldStyle} \hfill #1}}
\renewcommand{\date}[1]{{\addfontfeature{Numbers=OldStyle} #1}}
\renewcommand{\labelitemi}{}

\setmainfont[
  Ligatures={TeX,Common},
%  BoldFont={AGaramondPro-Semibold},
]{Corbel} % other options: Corbel, Palatino, Adobe Garmond Pro, TeX Gyre Common
\setsansfont[
  Ligatures={TeX,Common},
  Letters=SmallCaps,
  Color=660000,
]{Corbel}
\setmonofont{FontAwesome}

\begin{document}
\pagestyle{fancy} \setlength\headwidth{6.5in}
\rhead{\textsc{daniel a.~rothenberg—cv—\thepage{} of \pageref*{LastPage}}} \cfoot{}
\thispagestyle{empty}
\begin{adjustwidth}{-1in}{}
{\Large\textbf{
  {\textsc{%
    {\addfontfeature{Style=TitlingCaps}D}\kern-1.5ptaniel
    {\addfontfeature{Style=TitlingCaps}A}\kern-2pt.~%
    {\addfontfeature{Style=TitlingCaps}R}othenberg}
  }
 }
}
\hfill\hfill\hfill
{\small
  \begin{minipage}[b]{1.6in}
    \flushleft \footnotesize
    77 Massachusetts Avenue \\
    Building 54-1415 \\
    Cambridge, MA~~02139
  \end{minipage}
  \hfill
  \begin{minipage}[b]{1.6in}
    \flushright \footnotesize
    \href{tel:\myphone}{\myphone}~\faPhone \\
    \href{mailto:\myemail}{\myemail} ~\faEnvelope \\
    \href{https://www.twitter.com/\mytwitter}{@\mytwitter} ~\faTwitter \\
    \href{\mywebsite}{\mywebsiteshort} ~\faGlobe
  \end{minipage}
}\par
\hrulefill
\end{adjustwidth}
\reversemarginpar
\setlength\marginparwidth{0.85in}
\medskip
\mhead{Education}%
\textbf{Massachusetts Institute of Technology,} Cambridge, MA \newline
Ph.D., Dept. of Earth, Atmospheric and Planetary Sciences, \emph{Atmospheric Science} \rdate{\textsc{exp. Summer} 2016}
{\small
 \begin{itemize*}
  \item \emph{Committee}: Chien Wang, Dan Czizco, Paul O'Gorman, Steve Ghan
  \item \emph{Dissertation Title}: Impacts of Droplet Activation on Global Model Estimates of Aerosol-Cloud Interactions
%  \item Coursework:\newline
%    \begin{tabular}{ll}
%      \addlinespace\toprule
%
%      \bottomrule
%    \end{tabular}
 \end{itemize*}
}
Certificate; Science, Technology and Policy \rdate{\textsc{exp. Summer} 2016}

\medskip
\textbf{Cornell University,} Ithaca, NY \newline
B.S., Atmospheric Science, \emph{magna cum laude}, Honors in Research \rdate{2010}
{\small
 \begin{itemize*}
  \item \emph{Thesis Advisor}: Natalie Mahowald
  \item \emph{Thesis Title}: Volcano Impacts on Climate and Biogeochemistry
%  \item Selected Coursework:\newline
%    \begin{tabular}{ll}
%      \addlinespace\toprule
%
%      \bottomrule
%    \end{tabular}
 \end{itemize*}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % HONORS AND AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bigskip
\mhead{Honors and Awards}%
Outstanding Student Presentation Award ($\dagger$), AMS                          \rdate{2015} \newline
National Science Foundation Graduate Research Fellowship, NSF        \rdate{2012} \newline
National Defense Science And Engineering Fellowship, ASEE (\emph{declined}) \rdate{2012} \newline
Father James B. Macelwane Award in Meteorology, AMS                  \rdate{2011} \newline
Klein Fellowship, MIT-EAPS                                           \rdate{2011} \newline
Charney Prize, MIT-EAPS                                              \rdate{2011} \newline
Academic Excellence Award - Atmospheric Science, Cornell/CALS        \rdate{2011} \newline
Richard and Helen Hagermeyer Scholarship, AMS                        \rdate{2010} \newline
%Freshman Undergraduate Scholarship, AMS                              \rdate{2007} \newline
% others, maybe not appropriate anymore
%Valedictorian, duPont Manual High School                             \rdate{2007} \newline
%Eagle Scout, Troop 317, BSA                                          \rdate{2007} \newline

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % RESEARCH EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\medskip
\mhead{Research \newline Experience}%
\textbf{Program in Atmospheres, Oceans, and Climate,} MIT, Cambridge, MA \newline
\emph{Research Assistant} \rdate{2011-\textsc{present}}
\begin{itemize}[itemindent=-10pt]
\item Used novel uncertainty quantification techniques to develop emulator of droplet activation for patameterization in global models
\item Developed open-source, modular parcel modeling framework for studying droplet activation from diverse aerosol populations and for evaluating activation schemes
\item Used global climate models (CESM, CMIP5 archive, AEROCOM Indirect Effects Experiment) to study aerosol indirect effects and aerosol-cloud interactions
\item Participated in Fifth Ice Nucleation Workshop Part 2 in Karlsruhe, Germany; assisted with the operation of the Spectrometer for Ice Nucleation (SPIN) and developed software for automating the instrument and designing experiment setups
\end{itemize}

\medskip
\textbf{Department of Earth and Atmospheric Sciences,} Cornell University, Ithaca, NY \newline
\emph{Undergraduate Research Assistant} \rdate{2008-2011}
\begin{itemize}[itemindent=-10pt]
	\item Studied biogeochemical/climate processes and interactions with a coupled carbon-climate model
	\item Performed and analyzed fully-coupled model simulations studying transient climate change in the 20th century
\end{itemize}

\medskip
\textbf{Center for Multiscale Modeling of Atmospheric Processes,} Colorado State University, \newline Fort Collins, CO \newline
\emph{Summer Intern} \rdate{\textsc{summer} 2010}
\begin{itemize}[itemindent=-10pt]
	\item Implemented end evaluated a baroclinic instability test case on a very high resolution global atmospheric dynamical core, identifying numerical problems
	\item Developed novel visualization tools for analyzing model data on geodesic computational meshes
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % PROFESSIONAL ACTIVITIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bigskip
\mhead{Professional \newline Activities}
\textbf{NSPG}, STEM on the Hill Congressional Visits Day, Washington, DC \rdate{\textsc{Spring} 2015}\newline
\textbf{AMS}, Weather Water and Climate Day, Washington, DC \rdate{\textsc{June} 2015} \newline
\textbf{AMS}, 7th Annual Geosciences Congressional Visits Day, Washington, DC \rdate{\textsc{September} 2014} \newline
\textbf{AMS}, Summer Policy Colloquium, Washington, DC \rdate{\textsc{summer} 2014} \newline
\textbf{MIT/SPI}, ASTE Science/Engineering Congressional Visits Day, Washington, DC \rdate{\textsc{spring} 2012/2014} \newline
\textbf{CMMAP/NCAR/NCEP}, Summer School on Atmospheric Modeling, Boulder, CO \rdate{\textsc{summer} 2010} \newline
%Instructor: Ron Prinn

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % TEACHING EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bigskip
\mhead{Teaching \newline Experience}%
\emph{Graduate} \newline

\textbf{Global Warming Science (12.340x)} \rdate{\textsc{spring} 2016} \newline
MIT-EdX and MIT, Department of Earth, Atmospheric and Planetary Sciences \newline
Teaching Assistant
\newline

\textbf{Atmospheric Physics and Chemistry (12.806/12.306)} \rdate{\textsc{spring} 2014-2015} \newline
MIT, Department of Earth, Atmospheric, and Planetary Sciences \newline
Teaching Assistant
%Instructor: Ron Prinn
\newline

\textbf{``Climate Change Science'' IAP Seminar} \rdate{\textsc{winter} 2011-2013} \newline
MIT, Joint Program on the Science and Policy of Global Change \newline
Lecturer

\medskip
\emph{Undergraduate} \newline
\textbf{Object-Oriented Programming and Data Structures (CS 2110)} \rdate{2009-2010} \newline
Cornell University, Department of Computer Science \newline
Course Consultant, Teaching Asssitant
%Instructor: Dexter Kozin

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % LEADERSHIP / SERVICE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bigskip
\mhead{Leadership and Service}%
\textbf{Student Conference Planning Committee} \newline
American Meteorological Society
\begin{itemize}
	\item Co-Chair \rdate{2015-2016}
	\item Session Chair \rdate{2011-2014}
\end{itemize}

\medskip
\textbf{Graduate Climate Conference Executive Committee} \newline
MIT/Woods Hole Oceanographic Institution/University of Washington
\begin{itemize}
	\item Co-Chair \rdate{2013}
  \item Steering Committee Member \rdate{2015}
  \item Advisor; Fundraising Chair \rdate{2015}
\end{itemize}

\medskip
\textbf{Atmospheric Sciences Seminar Committee} \newline
MIT Department of Earth, Atmospheric, and Planetary Sciences
\begin{itemize}
  \item Member \rdate{2012-2014}
  \item Chair \rdate{2014-2015}
\end{itemize}

\medskip
\textbf{Reviewer}
\begin{itemize}
  \item Journal of Geophysical Research - Atmospheres \rdate{2014-\textsc{present}}
\end{itemize}

\medskip
\textbf{Science Policy Initiative Executive Committee} \rdate{2013-\textsc{present}} \newline
Massachusetts Institute of Technology

\medskip
\textbf{/r/science Moderator} \rdate{2010-2011, 2016-\textsc{present}} \newline
Reddit (volunteer)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % EMPLOYMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bigskip
\mhead{Work \newline Experience}%
\textbf{Google / Ravenbrook Software} \rdate{2011} \newline
Contract Developer
\begin{itemize}[itemindent=-10pt]
	\item Ported a high-performance algorithm used in surface temperature analysis at the National Climatic Data Center from Fortran to Python
	\item Developed extensive documentation and test suite for algorithm
	\item Identified and corrected numerous numerical and programming bugs and validated algorithm against synthetic datasets
\end{itemize}

\medskip
\textbf{Orion Network Services} \rdate{2006-2007} \newline
Software Developer
\begin{itemize}[itemindent=-10pt]
	\item Developed an online river flooding visualization tool for NOAA using ArcGIS and other scripting tools
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bigskip
\mhead{Publications}%
\emph{Refereed/Peer-Reviewed} \newline
\begin{enumerate}[itemindent=-10pt]

 \item \textbf{Rothenberg, Daniel} and Chien Wang: Development and Evaluation of a metamodel for droplet activation in a mixing-state-resolving coupled aerosol-climate model. (\emph{in prep})

 \item \textbf{Rothenberg, D.}, Wang, C., and Avramov, A.: Impact of activation parameterizations on aerosol-cloud interactions in a global climate model. (\emph{in prep})

 \item Garimella, S., \textbf{Rothenberg, D.}, Wang, C., Cziczo, D. J.: How uncertainty in field measurements of ice nucleating particles influences modeled cloud forcing. (\emph{in prep})

 \item Garimella, S., Kristensen, T. B., Ignatius, K., Welti, A., Voigtländer, J., Kulkarni, G. R., Sagan, F., Kok, G. L., Dorsey, J., Nichman, L., \textbf{Rothenberg, D.}, Rösch, M., Kirchgäßner, A., Ladkin, R., Wex, H., Wilson, T. W., Ladino, L. A., Abbatt, J. P. D., Stetzer, O., Lohmann, U., Stratmann, F., and Cziczo, D. J.: \href{http://www.atmos-meas-tech.net/9/2781/2016/amt-9-2781-2016.html}{The SPectrometer for Ice Nuclei (SPIN): An instrument to investigate ice nucleation}, Atmos. Meas. Tech, doi:10.5194/amt-9-2781-2016, 2016.

 \item \textbf{Rothenberg, Daniel} and Chien Wang: \href{http://dx.doi.org/10.1175/JAS-D-15-0223.1}{Metamodeling of Droplet Activation for Global Climate Models}, J. Atmos. Sci., 73, 1255–1272. doi:10.1175/JAS-D-15-0223.1, 2016

 \item \textbf{Rothenberg, D.}, Mahowald, N., Lindsay, K., Doney, S. C., Moore, J. K., and Thornton, P.: \href{http://dx.doi.org/10.5194/esd-3-121-2012}{Volcano impacts on climate and biogeochemistry in a coupled carbon–climate model}, Earth Syst. Dynam., 3, 121-136, doi:10.5194/esd-3-121-2012, 2012.

 \item Mahowald, N., Lindsay, K., \textbf{Rothenberg, D.}, Doney, S. C., Moore, J. K., Thornton, P., Randerson, J. T., and Jones, C. D.: \href{http://dx.doi.org/10.5194/bg-8-387-2011}{Desert dust and anthropogenic aerosol interactions in the Community Climate System Model coupled-carbon-climate model}, Biogeosciences, 8, 387-414, doi:10.5194/bg-8-387-2011, 2011.

 \item Mahowald, N. M., Kloster, S., Engelstaedter, S., Moore, J. K., Mukhopadhyay, S., McConnell, J. R., Albani, S., Doney, S. C., Bhattacharya, A., Curran, M. A. J., Flanner, M. G., Hoffman, F. M., Lawrence, D. M., Lindsay, K., Mayewski, P. A., Neff, J., \textbf{Rothenberg, D.}, Thomas, E., Thornton, P. E., and Zender, C. S.: \href{http://dx.doi.org/10.5194/acp-10-10875-2010}{Observed 20th century desert dust variability: impact on climate and biogeochemistry}, Atmos. Chem. Phys., 10, 10875-10893, doi:10.5194/acp-10-10875-2010, 2010.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % PRESENTATIONS / TALKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bigskip
\mhead{Presentations \newline and \newline Talks}%
%\emph{Please see \href{http://danielrothenberg.com/about/publicationspresentations}{my personal homepage} for a complete list of recent talks}
%\bigskip
%\begin{comment}
\emph{Conference Posters}
\medskip
\begin{itemize}[itemindent=-10pt]

 \item \textbf{Rothenberg, D.}, Wang, C. and Avramov, A.: Impacts of Droplet Activation on Fast and Slow Responses in a Coupled Aerosol-Climate Model. Gordon Research Seminar/Conference. Bates College, ME. 2015 | \href{http://figshare.com/articles/poster_pdf/1534717}{PDF}

 \item \textbf{Rothenberg, Daniel} and Chien Wang. Assessing the sensitivity of global aerosol indirect effects to activation treatment. Graduate Climate Conference, University of Washington. Seattle, WA. 2014

 \item \textbf{Rothenberg, Daniel} and Chien Wang. \href{https://ams.confex.com/ams/14CLOUD14ATRAD/webprogram/Paper250349.html}{A Novel Parameterization of Droplet Activation Suitable for Global Climate Models.} 14th Conference on Cloud Physics, American Meteorological Society. Boston, MA. 2014 |  \href{http://figshare.com/articles/A_Novel_Parameterization_of_Droplet_Activation_Suitable_for_Global_Climate_Models/1085984}{PDF}

 \item \textbf{Rothenberg, Daniel} and Chien Wang. \href{http://figshare.com/articles/A_Novel_Parameterization_of_Droplet_Activation_Suitable_for_Global_Climate_Models/1085984}{A Novel Parameterization of Droplet Activation Suitable for Global Climate Models.} CENSAM Workshop. Singapore. 2014

 \item \textbf{Rothenberg, Daniel} and Chien Wang. \href{https://ams.confex.com/ams/94Annual/webprogram/Paper240205.html}{Evaluating the Role of Aerosol Mixing State in Cloud Droplet Nucleation using a New Activation Parameterization}. 94th Annual Meeting of the American Meteorological Society, Sixth Symposium on Aerosol-Cloud-Climate Interactions. Atlanta, GA. 2013. | \href{https://figshare.com/articles/AMS_2014_Evaluating_the_Role_of_Aerosol_Mixing_State_in_Cloud_Droplet_Nucleation_towards_Developing_a_New_Activation_Parameterization/918655}{PDF}

 \item \textbf{Rothenberg, Daniel} and Chien Wang. Global Climate Response to Enhanced Anthropogenic Aerosol Emissions in a ``hazy world'' Experiment with the CESM. 6th Graduate Climate Conference. 2013.

 \item \textbf{Rothenberg, Daniel} and Ross Heikes. \href{https://ams.confex.com/ams/91Annual/webprogram/Paper180796.html}{A baroclinic instability test case on an anelsatic dynamical core}. 91st Annual Meeting of the American Meteorological Society, 24th Conference on Weather and Forecasting/20th Conference on Numerical Weather Prediction. Seattle, WA. 2012.
\end{itemize}

\bigskip
\emph{Invited Talks}
\medskip
\begin{itemize}[itemindent=-10pt]
\item \textbf{Rothenberg, D.}, Avramov, A., Wang, C., Garimella, S., Wolf, M., and Cziczo, D. Understanding Fundamental Aerosol-Cloud Interactions and their Contributions to the Aerosol Indirect Effect. NOAA Geophysical Fluid Dynamics Laboratory. Princeton, NJ. 2016
\end{itemize}

\bigskip
\emph{Conference Talks}
\medskip
\begin{itemize}[itemindent=-10pt]

 \item \textbf{Rothenberg, Daniel}. \href{https://ams.confex.com/ams/96Annual/webprogram/Paper286193.html}{A Python-based Parcel Model Framework for Studying Aerosol-Cloud Processes}. Sixth Symposium on Advances in Modeling and Analysis Using Python. New Orleans, 2016. | \href{https://figshare.com/articles/A_Python-based_Parcel_Model_Framework_for_Studying_Aerosol-Cloud_Processes/3475241}{PDF}

 \item \textbf{Rothenberg, Daniel}, Chien Wang and Alexander Avramov. On the Sensitivity of Model-derived Estimates of Aerosol Indirect Effects and Forcings to Activation Schemes. 96th Annual Meeting of the American Meteorological Society, Eighth Symposium on Aerosol-Cloud-Climate Interactions. New Orleans, LA. 2016. \href{https://ams.confex.com/ams/96Annual/webprogram/Paper289914.html}{Program Link}

 \item[$\dagger$] \textbf{Rothenberg, Daniel}, Chien Wang and Alexander Avramov. \href{https://ams.confex.com/ams/95Annual/webprogram/Paper268747.html}{Evaluating Advanced Aerosol Activation Treatments in a Coupled Climate/Mixing-State Resolving Aerosol Model}. 95th Annual Meeting of the American Meteorological Society, 7th Symposium on Aerosol-Cloud-Climate Interactions. Phoenix, AX. 2015. | \href{https://figshare.com/articles/Evaluating_Advanced_Aerosol_Activation_Treatments_in_a_Coupled_Climate_Mixing-State_Resolving_Aerosol_Model/3475226}{PDF}

 \item \textbf{Rothenberg, Daniel} and Chien Wang. Evaluating the Role of Aerosol Mixing State in Cloud Droplet Nucleation using a New Activation Parameterization. American Geophysical Union Fall Meeting, (A34D-03). 2013.

 \item \textbf{Rothenberg, Daniel} and Chien Wang. \href{http://figshare.com/articles/AMS_2014_Evaluating_the_Role_of_Aerosol_Mixing_State_in_Cloud_Droplet_Nucleation_towards_Developing_a_New_Activation_Parameterization/918655}{Cloud and Climate Impacts in a Hazy World Simulation}. 93rd Annual Meeting of the American Meteorological Society, 5th Symposium on Aerosol-Cloud-Climate Interactions. Austin, TX. 2014.

 \item \textbf{Rothenberg, Daniel} and Nick Barnes. \href{https://ams.confex.com/ams/92Annual/webprogram/Paper198219.html}{Lessons From Deploying the USHCN Pairwise Homogenization Algorithm in Python}. 92nd Annual Meeting of the American Meteorological Society, Second Symposium on Advances in Modeling and Analysis Using Python. New Orleans, LA. 2012
\end{itemize}

\vspace{0.1cm}

\emph{\small{Note: annotations ($\dagger$, etc) correspond to ``Honors and Awards'' section.}}

%\end{comment}
%\emph{Other}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % PROFESSIONAL AFFILIATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bigskip
\mhead{Professional \newline Affiliations}%
American Meteorological Society \rdate{2010-\textsc{present}} \newline
American Physical Society  \rdate{2011-\textsc{present}} \newline
American Geophysical Union \rdate{2013-\textsc{present}} \newline
Association for Computing Machinery \rdate{2011-2012} \newline

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % TECHNICAL SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\medskip
\mhead{Technical \newline Skills}

\emph{\small{Note: Please visit my \href{http://www.github.com/darothen/}{Github} page for examples of projects implementing these skills}}\newline

\begin{itemize}
  \item \textbf{Data Science} - Python (\emph{expert}), Matlab, Java, d3.js, git/hg/svn
  \item \textbf{Numerical Modeling} - Python/Cython/Numba, legacy/modern Fortran, C/C++/CUDA (\emph{familiar}); emphasis on scientific software design and application of software engineering to numerical codes/tools
  \item \textbf{Atmospheric/Climate Models} - \href{http://www.github.com/darothen/parcel_model}{pyrcel}, CESM, MIT-CRM, WRF (\emph{familiar})
  \item \textbf{High-Performance Computing} - NCAR supercomputers (bluefire/yellowstone); previously worked on NERSC and Oak Ridge systems
  \item \textbf{Web Design} - Django, ghost, HTML/CSS
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % PERSONAL INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\medskip
\mhead{Personal \newline Interests}%
Violin performance - classical (18 years),
Winter sports,
Backpacking/hiking,
Software development/
engineering,
Meteorology education/forecasting,
Debate and rhetoric,
Science/Innovation policy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % END NOTES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bigskip
\begin{center}
  \emph{Last Updated}: \today
\end{center}

\newpage

\end{document}
